### 2015-03-13 doc/notebook/2015-03-13_Archaeal_data_acquisition.Rmd
Remove folder paths for time being

metadata <- read.table(file="data/raw/metadata.nds", sep="\t", stringsAsFactors=FALSE,
                            col.names=metadata_fields, fill=TRUE, na.strings="",
                            quote="")
rownames(metadata) <- paste(metadata$name, metadata$acc, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

```{r}
bad_accnos_data <- read.table(file="data/process/archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="data/process/all_archaea.good.metadata", quote=F, sep="\t")
```

>>>>

metadata <- read.table(file="archaea_metadata.nds", sep="\t", stringsAsFactors=FALSE,
                            col.names=metadata_fields, fill=TRUE, na.strings="",
                            quote="")
rownames(metadata) <- paste(metadata$name, metadata$acc, sep=".")
metadata <- metadata[,-c(1,2)]
```

@@

```{r}
bad_accnos_data <- read.table(file="archaea.bad.accnos", col.names=c("name.accnos", "reason"))
bad_accnos <- bad_accnos_data$name.accnos
metadata_good <- metadata[-c(bad_accnos),]
write.table(metadata_good, file="all_archaea.good.metadata", quote=F, sep="\t")
```
